Modern Graph Generators: A Survey

### 2018-09-09 comparison.tex
Minor changes, extension of tables
Adding of missing entries of the tables, creating a draft of matrix
expressing overlapping

In order to provide the reader with a quick preview of the generators and thus finding the target solutions easily, we start the survey with classification and comparative study of the existing tools. There are various ways how to classify them. We first overview approaches used in related work and then we introduce ours. As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.

In general, the graph data generators can be classified according to various criteria. Paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.

@@

At first we classify the generators on the basis of the respective application domains or user communities. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains. In particular, we show:

\begin{itemize}
\item Characteristics of the domain - its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key configuration options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \textit{properties} of the graph,
    \item supported types of \textit{distributions} used for generating of the data,
    \item \textit{output format} of the produced graph,
    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
  \end{itemize}
\end{itemize}

As we can see...

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{8}{*}{\rot{\textbf{General}}}
  & graph500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
  & Preferential Attachment~\cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline %  ======================  Semantic web
\multirow{22}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output format}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{Graph DBs}}}
 & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
 \cline{2-10}
& graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
 \cline{2-10}
 & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\hline
\hline %  ======================   social networks
\multirow{9}{*}{\rot{\textbf{Social networks}}}
& LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
& S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
& SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
\cline{2-10}
& Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\cline{2-10}
& Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
\cline{2-10}
& BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\hline
\hline   % ======================   graph analytics
\multirow{5}{*}{\rot{\textbf{Analytics}}}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\hline   %  ======================  streaming
\multirow{5}{*}{\rot{\textbf{Streaming}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & & &    \\
\cline{2-10}
  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

>>>>

In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with classification and comparative study of the existing tools. In general, there are various ways how to classify them. We first overview approaches used in related work and then we introduce our approach. As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy differs too.

The graph data generators can be classified according to various criteria. For example, paper~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. Given a degree distribution (typically following a power law), \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) try to find a graph that matches it, but without giving any insights about the graph or trying to match other criteria (like, e.g., small diameter, eigenvalues etc.). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) try to find simple mechanisms to generate graphs that match a property of the real graphs and, typically, the power law degree distribution.

@@

\subsection{Classification}

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, and (6) graph data steaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Tables~\ref{tab:comparisonCharacteristicsA},~\ref{tab:comparisonCharacteristicsB}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``An.'' stands for graph analytics, ``St.'' stands for graph streaming.} In particular, we show:

\begin{itemize}
\item Characteristics of the domain -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} operations (if provided), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key configuration options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \textit{properties} of the graph,
    \item supported types of \textit{distributions} used for generating of the data,
    \item \textit{output format} of the produced graph, and
    \item  whether the generator is \textit{distributed} and thus enables more efficient data generation.
  \end{itemize}
\end{itemize}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part A)} {
\begin{tabular}{| c | p{2.2cm} | p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline   % ====================== general graphs
\multirow{7}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & fixed & & Y & N & Y &  & &  N  \\
\cline{2-10}
   & R-MAt & fixed & & Y & N & Y & power-law & &  N  \\
\cline{2-10}
  & GraphGen & & & & & & & &    \\
\cline{2-10}
  & Graph 500  & fixed & & Y & N & Y & power-law & &  Y  \\
\cline{2-10}
  & BTER & & & & & & & &    \\
\cline{2-10}
  & Darwini & & & & & & & &    \\
%  & Watts-Strogatz~\cite{watts1998collective} & fixed & & Y & N & Y &  & &  N  \\
%\cline{2-10}
\hline
\hline %  ======================  Semantic web
\multirow{20}{*}{\rot{\textbf{Semantic web}}}
 & LUBM & fixed & university  & fixed & N & Y & random (LCG) &  RDF & N   \\
\cline{2-10}
 & LBBM & extracted & Lehigh University BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
\cline{2-10}
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\
\cline{2-10}
 & IIMB & fixed & movies  & N & N & Y & random &  RDF & N   \\
\cline{2-10}
 & BSBM & fixed & e-commerce  & fixed & N & Y & mostly normal &  RDF, relational & N   \\
\cline{2-10}
 & SP$^2$Bench & fixed & DBLP  & fixed & N & Y & based on DBLP  & RDF & N   \\
\cline{2-10}
 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\
\cline{2-10}
 & DBPSB & extracted & DBpedia &  templates & N & Y & random &  RDF & N   \\
\cline{2-10}
 & LODIB & fixed & e-commerce &  N & N & Y & 44 types &  RDF & N   \\
\cline{2-10}
 & SIB & fixed & social network &  mixes & mix & Y & from real-world data &  RDF & N   \\
\cline{2-10}
 & Geographica & fixed & OpenStreetMap  & fixed + templates  & N & Y & -- &  RDF & N   \\
\cline{2-10}
 & WatDiv & schema-driven & user-defined  & templates & N & Y & uniform, normal, Zipfian &  RDF & N   \\
\cline{2-10}
 & RBench & extracted & DBLP, Yago  & templates & N & Y & from real-world data &  RDF & N  \\
\cline{2-10}
 & LDBC SPB & fixed & media  & mixes & N & Y & power law, skewed values, value correlation &  RDF & N  \\
\cline{2-10}
 & LinkGen & & & & & & & & \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsA}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & & & & &    \\
\cline{2-10}
 & \cite{Yao2011} & & & & & & & &    \\
\cline{2-10}
 & LinkBench & & & & & & & &    \\
\cline{2-10}
 & S3G2 & Y & Y  & N &  & Y & Facebook-like  &  CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & & & & & & & &    \\
\cline{2-10}
 & LDBC SNB  & Y & Y &   generated &  & Y & Facebook-like &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & & & & & & & &    \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
%\cline{2-10}
% & Darwini  & N & N &   N &  & N & user-defined &  ? & Y   \\
%\cline{2-10}
% & BTER  & N & N &   N &  & N & user-defined &  ? & Y  \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & & & & & & & &    \\
\cline{2-10}
  & Graphalytics & & & & & & & &    \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

\subsection{Overlapping}

As we have mentioned, the basic classification we use in this paper is  based on a relatively vague division of the generators on the basis of the current application domains or research areas. In addition, some of the generators are either general or have features applicable in other domains. So the classes can overlap, as depicted in Table~\ref{tab:overlapping}.

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & x & & & & & \\
\cline{2-8}
   & R-MAt    & x & & & & & \\
\cline{2-8}
  & GraphGen  & x & & & & & \\
\cline{2-8}
  & Graph 500 & x & & & & & \\
\cline{2-8}
  & BTER      & x & & & & & \\
\cline{2-8}
  & Darwini   & x & & & & & \\
%  & Watts-Strogatz~\cite{watts1998collective}  & x & & & & & \\
%\cline{2-8}
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & x & & & & \\
\cline{2-8}
 & LBBM  & & x & & & & \\
\cline{2-8}
 & UOBM  & & x & & & & \\
\cline{2-8}
 & IIMB & & x & & & & \\
\cline{2-8}
 & BSBM & & x & & & & \\
\cline{2-8}
 & SP$^2$Bench & & x & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
\cline{2-8}
 & DBPSB & & x & & & & \\
\cline{2-8}
 & LODIB & & x & & & & \\
\cline{2-8}
 & SIB & & x & & & & \\
\cline{2-8}
 & Geographica & & x & & & & \\
\cline{2-8}
 & WatDiv & & x & & & & \\
\cline{2-8}
 & RBench & & x & & & & \\
\cline{2-8}
 & LDBC SPB & & x & & & & \\
\cline{2-8}
 & LinkGen & & x & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & x & & & \\
\cline{2-8}
  & gMark & & & x & & & \\
\cline{2-8}
  & graphGen & & & x & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & x & & \\
\cline{2-8}
 & LinkBench  & & & & x & & \\
\cline{2-8}
 & S3G2  & & & & x & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
\cline{2-8}
 & LDBC SNB   & & & & x & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & x & & \\
%\cline{2-8}
% & SNG  & & & & x & & \\
%\cline{2-8}
% & Forest Fire  & & & & x & & \\
%\cline{2-8}
% & Darwini & & & & x & & \\
%\cline{2-8}
% & BTER  & & & & x & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & x & \\
\cline{2-8}
  & Graphalytics & & & & & x & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & x\\
\cline{2-8}
  & RSPLab & & & & & & x \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}
